A More Complete Algebra for File Synchronization

### 2015-11-14 2015/paper.tex
Fresh start: new definitions for the algebra

\usepackage{alltt}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{setspace}
% \usepackage{fullpage}
\usepackage{graphicx}
% \usepackage{afterpage}

\usepackage{centernot}
\usepackage{tikz}

% TODO Use cleveref to add prefix to references

\newcommand{\setv}{\mathcal{V}}
\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
\newcommand{\setf}{\setvx{F}}
\newcommand{\setd}{\setvx{D}}
\newcommand{\setb}{\setvx{\empt}}
\newcommand{\setp}{\mathcal{P}}
\newcommand{\empt}{\bot}
\newcommand{\parent}{\mathtt{parent}}
\newcommand{\toppath}{\mathtt{None}} % return value of parent()
\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
\newcommand{\FS}{\Phi} % a filesystem
\newcommand{\GS}{\Xi} % another filesystem
\newcommand{\pp}{p^\uparrow} % parent path
\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p

@@

\newcommand{\eqext}{\sqsubseteq}
\newcommand{\eqnrw}{\sqsupseteq}
\newcommand{\nequiv}{\not\equiv}
\newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
\newcommand{\wrnrw}{\stackrel{\mathtt{br}}{\sqsupseteq}}
\newcommand{\coworks}{\circ}
\newcommand{\ncoworks}{\centernot\circ}

@@

@@

@@

To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
if $\setb = \{\empt\}$ then:
\[ \setv = \setb \cup \setf \cup \setd \]
The tree propety can then be defined as
\[ \forall \FS, p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]

@@

The exact behaviour of our commands is as follows:
\begin{itemize}
\item $\cbrk\FS = \fsbroken$
\item
All commands have the generic form $\cxy(p,V_Y)$ where
$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
At times we omit $V_Y$ if there is only one suitable value.

Let us introduce the following notation for a filesystem derived from $\FS$:
\[ \FS\{p\mapsto V\}(q) :=
   \begin{cases}
   V &\mbox{if~} q=p\\
   \FS(q) &\mbox{otherwise.}
   \end{cases}
\]

Then
\[ \cxy(p,V_Y)\FS = 
   \begin{cases}
   \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} \FS(p)\not\in\setvx{X}\\
   \fsbroken &\mbox{if~} \FS\{p\mapsto V_Y\} \mbox{~violates the tree property}\\
   \FS\{p\mapsto V_Y\} &\mbox{otherwise.}
   \end{cases}
\]
\end{itemize}

@@

Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
a set of axioms in a sound and complete algebra and use the algebra effectively we at times needed to take into account
the relationship between the paths of the commands in the pair, $p$ and $q$.
As the relationship between the paths determine how the commands affect the filesystem
and its tree property, 
and again in line with the aim of providing as much information as possible for the algebra,
we encode this relationship in the pair of commands. The possible relationships we
consider are as follows.

\begin{description}
\item[Same.] Paths that are the same ($p=q$). If the two commands affect the same path, the pair of commands
will clearly behave differently than if the paths are different.
%
\item[Unrelated.] Paths that are not \emph{directly} related,
that is, where $\parent(p)\neq q$ and $\parent(q)\neq p$. 
In this case modifying the filesystem at one path is not going
to affect the outcome of the command on the other path.
The two commands will therefore commute and the pair will be reversible.
We will denote a path separate from $p$ with $\np$.
%
\item[Directly related.] Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
For simplicity, we will write $\pp$ for $\parent(p)$.
Some of these command pairs will not be reversible.
For example, $[\cbd(\pp,D);\cbf(p,F)]$ will work on some filesystems,
while $[\cbf(p,F);\cbd(\pp,D)]$ will break all filesystems.
\end{description}

One may think that we may be able to specify more about the reversibility
or possible simplification of a pair of commands in the last group if we also
knew whether the child path $p$ was the only (non-empty) child of its parent.
However, it is easy to see that encoding this information in a pair
is not going to enrich our algebra as, for example,
the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
is exactly the same as that of the more generic
$[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
$p$ is not the only child as it violates its preconditions, but so will
the generic pair.

@@

In summary, we have pairs of commands
of the following forms:
\begin{description}
\item[Unrelated.] \( [\cxy(p,V_Y); \czw(\np,V_W)] \)
\item[Same.] \( [\cxy(p,V_Y); \czw(p,V_W)] \)
\item[Down.] \( [\cxy(\pp,V_Y); \czw(p,V_W)] \)
\item[Up.] \( [\cxy(p,V_Y); \czw(\pp,V_W)] \)
\end{description}

@@

In order to reason about sequences of commands, we define \emph{algebraic laws} on
commands. We use formal logic to build a proof system which is sound and
complete for its intended interpretation.

Similarly to \cite{NREC:alg}, we have two kinds of judgements
for sequences \(S_1\) and \(S_2\):
\begin{mydef}
\(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
\(S_2\)}. Its intended interpretation is that they act in the same way on all
filesystems. It is a commutative and transitive relation.
\end{mydef}
\begin{mydef}
\(S_1\eqext S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
interpretation is that they act in the same way on all
filesystems that \(S_1\) does not break. It is a transitive relation.
\end{mydef}

We have inference rules for the two judgements,
which make it possible to derive new statements from the axioms or other statements.
These are:

\emph{For any sequences \(S_1, S_2, S, S'\):}
\begin{itemize}
\item \(S_1\equiv S_2 \Rightarrow S;S_1;S'\equiv S;S_2;S'\)
\item \(S_1\eqext S_2 \Rightarrow S;S_1;S'\eqext S;S_2;S'\)
\item \(S_1\equiv S_2 \Rightarrow S_1\eqext S_2\).
\end{itemize}

@@

\begin{description}
\item[Unrelated.] If the two paths in the pair are not directly related, then
the commands commute with an equivalence and they will not break every filesystem:
\begin{align*}
[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)] \\
&\nequiv \cbrk
\end{align*}
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), the
the commands cannot be reversed. Instead:
   \begin{description}
   \item[Break.]
   The pair will break every filesystem if $Z\ne Y$, that is, if the second
   command expects a type of value different from the one left by the first command.
   \item[Simplified by extension.]
   Otherwise, the pair will simplify to a single or no commands
   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
   \begin{gather*}
   % bf=fb Sp
            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
   % bd=db Sp
            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
   % db=bd Sp
            [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
   % df=fd Sp
            [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
   \end{gather*}
   \item[Simplified by equivalence.]
   In all other cases, the commands are equivalent to a single command
   replacing the input of the first command with the output of the second:
   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
   \end{description}
%
\item[Down.]
These are the pairs in which the first command is applied to the parent of the path
of the second command.
   \begin{description}
   \item[Construction.] There are pairs in this group to which no law applies:
   the commands do not commute or break every filesystem, and cannot be simplified.
   We call these ``construction'' pairs:
   \begin{gather*}
   % bd>bf
            [\cbd(\pp, D); \cbf(p, F)] \\
   % bd>bd
            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
   % fd>bf
            [\cfd(\pp, D); \cbf(p, F)] \\
   % fd>bd
            [\cfd(\pp, D_1); \cbd(p, D_2)]
   \end{gather*}
   \item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
   \begin{gather*}
   [\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
   \end{gather*}
   \item[Break.] All other pairs break every filesystem, e.g.:
   \begin{gather*}
   [\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
   \end{gather*}
   \end{description}
%
\item[Up.]
The final group of pairs are the ones in which the path in the second
command is the parent of the one in the first.
These behave similarly to the previous group. 
   \begin{description}
   \item[Desctruction.] There are
   so-called ``destruction'' pairs to which no law applies:
   \begin{gather*}
   % fb<db ??
            [\cfb(p); \cdb(\pp)] \\
   % fb<df ??
            [\cfb(p); \cdf(\pp, F)] \\
   % db<db ??
            [\cdb(p); \cdb(\pp)] \\
   % db<df ??
            [\cdb(p); \cdf(\pp, F)]
   \end{gather*}
   \item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
   \item[Break.] All other pairs break every filesystem.
   \end{description}
\end{description}

@@

\begin{mydef}{Minimal set / sequence}
By a minimal set or sequence of commands we mean a set / sequence in which
there is at most one command on every path.
\end{mydef}

@@

\begin{myax}$A\coworks B \Rightarrow A\nequiv\cbrk$\end{myax}
\begin{myax}$A\eqext B \Rightarrow A\wrext B$\end{myax}
\begin{myax}\label{axiom:wrextpostfix}$[A;S] \wrext A$\end{myax}
\begin{myax}$A\coworks B\wrext C \Rightarrow A\coworks C$\end{myax}
\begin{myax}\label{axiom:ncowwrnrw}$A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$\end{myax}

\begin{mylem}\label{lemma:ncowpostfix}$A\ncoworks B \Rightarrow [A;S]\ncoworks B$\end{mylem}
\begin{proof}From axioms \ref{axiom:wrextpostfix} and \ref{axiom:ncowwrnrw}\end{proof}

% \begin{myax}$\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ if $X\neq Z$\end{myax}

@@

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
and $\FS_B:=B\FS$, then our aim is to define sequences of commands $A^R$ and $B^R$
so that $B^R\FS_A$ and $A^R\FS_B$ would be as close to each other as possible.

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $A^R = \ordered{A\setminus B}$ and $B^R = \ordered{B\setminus A}$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$A^R = \ordered{A^{R*}}$  where $A^{R*} \subset A\setminus B$
and $B^R = \ordered{B^{R*}}$ where $B^{R*} \subset B\setminus A$ 
so that $A^R\FS_B\neq\fsbroken$ and $B^R\FS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $A^R$ or $B^R$ will break the filesystems.

@@

\begin{mydef}{Reconciliation}\label{def:reconciliation}
\[ A^R = \ordered{\{c| c\in A\setminus B \wedge \forall c'\in B\setminus A: [c;c']\equiv[c';c]\}} \]

In other words, the sequence $A^R$ we apply to $\FS_B$ are all commands from $A\setminus B$
that commute with every command in $B\setminus A$.
This is equivalent to saying that those commands are selected from $A\setminus B$
whose paths are unrelated to the paths of the commands in $B\setminus A$.
\end{mydef}

Now we prove that $A^R\FS_B\neq\fsbroken$.

@@

If $B$ has a command on $q$, then
from lemma \ref{lemma:neighbour}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
and from lemmas \ref{lemma:minextset} and \ref{lemma:minextorder} we know that $B'\equiv B$.
From the construction and destruction laws we also know that a command on $q$
must precede $\cxy(p, V_Y)$ just as it does so in $A$.

@@

As $A\coworks B$, 
from lemma \ref{lemma:cowinputmatch}
we know that $Q=Z$.

@@

We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
are at the beginning, and therefore 
from axiom \ref{axiom:wrextpostfix}
$A\wrext \ordered{A\cap B}$ and by symmetry $B\wrext \ordered{A\cap B}$.
\end{proof}

@@

>>>>

% \usepackage{alltt}
% \usepackage{comment}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{graphicx}
\usepackage{centernot}
\usepackage{tikz}
\usepackage{cleveref}

\newcommand{\setv}{\mathcal{V}}
\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
\newcommand{\setf}{\setvx{F}}
\newcommand{\setd}{\setvx{D}}
\newcommand{\setb}{\setvx{\empt}}
\newcommand{\setp}{\mathcal{P}}
\newcommand{\empt}{\bot}
\newcommand{\parent}{\mathtt{parent}}
\newcommand{\toppath}{\mathtt{None}} % return value of parent()
\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
\newcommand{\FS}{\Phi} % a filesystem
\newcommand{\GS}{\Xi} % another filesystem
\newcommand{\pp}{p\!\!\uparrow} % parent path

@@

\newcommand{\eqext}{\sqsubseteq}
\newcommand{\eqnrw}{\sqsupseteq}
\newcommand{\nequiv}{\not\equiv}

\newcommand{\works}{\dot{\mathbf{w}}}

% TODO: delete:
\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p TODO change this
\newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
\newcommand{\wrnrw}{\stackrel{\mathtt{br}}{\sqsupseteq}}
\newcommand{\coworks}{\circ}
\newcommand{\ncoworks}{\centernot\circ}

@@

\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
\newcommand{\reca}{\recchar{A}{B}{}} % Reconciliation
\newcommand{\recb}{\recchar{B}{A}{}}
\newcommand{\recaset}{\recchar{A}{B}{*}}
\newcommand{\recbset}{\recchar{B}{A}{*}}

@@

\crefname{mydef}{definition}{definitions}
\crefname{myax}{axiom}{axioms}
\crefname{mylem}{lemma}{lemmas}

@@

To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
if $\setb = \{\empt\}$ then:
\[ \setv = \setb \cup \setf \cup \setd \]
The tree propety can then be defined as
\[ \forall p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]

@@

\begin{mydef}
Using $\FS\{p\mapsto V\}$ we denote a filesystem derived from $\FS$:
\[ \FS\{p\mapsto V\}(q) :=
   \begin{cases}
   V &\mbox{if~} q=p\\
   \FS(q) &\mbox{otherwise.}
   \end{cases}
\]
\end{mydef}

The exact behaviour of our commands is as follows:
\begin{itemize}
\item $\cbrk\FS = \fsbroken$
\item
All other commands have the generic form $\cxy(p,V_Y)$ where
$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
At times we omit $V_Y$ if there is only one suitable value.
\[ \cxy(p,V_Y)\FS = 
   \begin{cases}
   \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} \FS(p)\not\in\setvx{X}\\
   \fsbroken &\mbox{if~} \FS\{p\mapsto V_Y\} \mbox{~violates the tree property}\\
   \FS\{p\mapsto V_Y\} &\mbox{otherwise.}
   \end{cases}
\]
\end{itemize}

@@

Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
a set of axioms in a sound and complete algebra and use the algebra effectively we at times needed to take into account
the relationship between the paths of the commands in the pair, $p$ and $q$.
As the relationship between the paths determine how the commands affect the filesystem
and its tree property, 
and again in line with the aim of providing as much information as possible for the algebra,
we encode this relationship in the pair of commands.

The possible relationships we
consider are as follows.

% One may think that we may be able to specify more about the reversibility
% or possible simplification of a pair of commands in the last group if we also
% knew whether the child path $p$ was the only (non-empty) child of its parent.
% However, it is easy to see that encoding this information in a pair
% is not going to enrich our algebra as, for example,
% the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
% is exactly the same as that of the more generic
% $[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
% $p$ is not the only child as it violates its preconditions, but so will
% the generic pair.

@@

@@

In the following sections $A,B,S$ and $T$ denote sequences of commands.
The first two relations echo the ones defined in \cite{NREC:alg}.

\begin{mydef}
$A\equiv B$ means that $A$ and $B$ are equivalent.
Its intended interpretation is that they behave in the same way on
all filesystems: $\forall \FS: A\FS=B\FS$.
It is a commutative and transitive relation.
\end{mydef}

\begin{mydef}
$A\eqext B$ means that $B$ extends $A$.
Its intended interpretation is that they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$
It is a transitive relation.
\end{mydef}

\begin{mydef}
$\works A$ means that $A$ does not break a filesystem.
Unlike the operators (TODO:?) defined above,
$\works$ ties to the same variable in the whole expression.
For example, the intended interpretation of
$\works A$ is $\exists \FS: A\FS\neq\fsbroken$,
and the intended interpretation of
$\works A\wedge\works B$ is $\exists \FS: A\FS\neq\fsbroken \wedge B\FS\neq\fsbroken$.

Clearly $\works A\Leftrightarrow A\nequiv\cbrk$.

TODO: This is temporary. Check in what expression $\works$ appears
to see if it can be simplified.
\end{mydef}

\begin{mydef}{Assertion command.}
A command is an assertion command if
for every filesystem it either breaks it or leaves it in the same state.
In our current algebra $\cbb$ and $\cdd$ are the only two assertion commands.
\end{mydef}

\begin{mydef}{Minimal set / sequence.}
A sequence or set of commands is minimal if it contains at most one command on every path.
\end{mydef}

\begin{mydef}{Simple set / sequence.}
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

\begin{myax}
$A\equiv B \Rightarrow A\eqext B$
\end{myax}

\begin{myax}
$A\equiv B \Rightarrow S;A;T\equiv S;B;T$
\end{myax}

\begin{myax}
$A\eqext B \Rightarrow S;A;T\eqext S;B;T$
\end{myax}

\begin{myax}
$A\eqext B \Rightarrow (\works A \Rightarrow \works B)$
\end{myax}

\begin{myax}\label{worksextpostfix}
$\works[A;S] \Rightarrow \works A$
\end{myax}

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $(\works A\wedge \works B)$,
and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
then their input types must match ($X=Z$).
TODO: Is this an axiom?
\end{mylem}

% ---------------------------------------------------------------

@@

\begin{description}
\item[Unrelated.] If the two paths in the pair are not directly related, then
the commands commute with an equivalence and they will not break every filesystem:
\begin{align*}
[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)]
\end{align*}
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), the
the commands cannot be reversed. Instead:
   \begin{description}
   \item[Break.]
   The pair will break every filesystem if $Z\ne Y$, that is, if the second
   command expects a type of value different from the one left by the first command.
   \item[Simplified by extension.]
   Otherwise, the pair will simplify to a single or no commands
   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
   \begin{gather*}
   % bf=fb Sp
            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
   % bd=db Sp
            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
   % db=bd Sp
            [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
   % df=fd Sp
            [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
   \end{gather*}
   \item[Simplified by equivalence.]
   In all other cases, the commands are equivalent to a single command
   replacing the input of the first command with the output of the second:
   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
   \end{description}
%
\item[Down.]
These are the pairs in which the first command is applied to the parent of the path
of the second command.
   \begin{description}
   \item[Construction.] There are pairs in this group to which no law applies:
   the commands do not commute or break every filesystem, and cannot be simplified.
   We call these ``construction'' pairs:
   \begin{gather*}
   % bd>bf
            [\cbd(\pp, D); \cbf(p, F)] \\
   % bd>bd
            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
   % fd>bf
            [\cfd(\pp, D); \cbf(p, F)] \\
   % fd>bd
            [\cfd(\pp, D_1); \cbd(p, D_2)]
   \end{gather*}
   \item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
   \begin{gather*}
   [\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
   \end{gather*}
   \item[Break.] All other pairs break every filesystem, e.g.:
   \begin{gather*}
   [\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
   \end{gather*}
   \end{description}
%
\item[Up.]
The final group of pairs are the ones in which the path in the second
command is the parent of the one in the first.
These behave similarly to the previous group. 
   \begin{description}
   \item[Desctruction.] There are
   so-called ``destruction'' pairs to which no law applies:
   \begin{gather*}
   % fb<db ??
            [\cfb(p); \cdb(\pp)] \\
   % fb<df ??
            [\cfb(p); \cdf(\pp, F)] \\
   % db<db ??
            [\cdb(p); \cdb(\pp)] \\
   % db<df ??
            [\cdb(p); \cdf(\pp, F)]
   \end{gather*}
   \item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
   \item[Break.] All other pairs break every filesystem.
   \end{description}
\end{description}

@@

@@

% TODO See above
\begin{myax}$A\coworks B \Rightarrow A\nequiv\cbrk$\end{myax}
\begin{myax}$A\eqext B \Rightarrow A\wrext B$\end{myax}
\begin{myax}\label{axiom:wrextpostfix}$[A;S] \wrext A$\end{myax}
\begin{myax}$A\coworks B\wrext C \Rightarrow A\coworks C$\end{myax}
\begin{myax}\label{axiom:ncowwrnrw}$A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$\end{myax}

\begin{mylem}\label{lemma:cowdelfix}$[A;S]\coworks B \Rightarrow A\coworks B$\end{mylem}
\begin{mylem}\label{lemma:ncowpostfix}$A\ncoworks B \Rightarrow [A;S]\ncoworks B$\end{mylem}
\begin{proof}From \cref{axiom:wrextpostfix,axiom:ncowwrnrw}\end{proof}

@@

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = \ordered{A\setminus B}$ and $\recb = \ordered{B\setminus A}$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca = \ordered{\recaset}$  where $\recaset \subset A\setminus B$
and $\recb = \ordered{\recbset}$ where $\recbset \subset B\setminus A$ 
so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $\reca$ or $\recb$ will break the filesystems.

@@

\begin{mydef}{Reconciliation}\label{def:reconciliation}
\begin{align*}
\recaset = \{c| & \\
& c\in A\setminus B \\
& \wedge \\
& \forall c'\in B\setminus A: [c;c']\equiv[c';c]\\
\} & \\
\reca = \ordered{\recaset}&
\end{align*}

In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
that commute with every command in $B\setminus A$.
This is equivalent to saying that those commands are selected from $A\setminus B$
whose paths are unrelated to the paths of the commands in $B\setminus A$.
\end{mydef}

Now we prove that $\reca\FS_B\neq\fsbroken$.

@@

If $B$ has a command on $q$, then
from \cref{lemma:neighbour}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
and from \cref{lemma:minextset,lemma:minextorder} we know that $B'\equiv B$.
From the construction and destruction laws we also know that a command on $q$
must precede $\cxy(p, V_Y)$ just as it does so in $A$.

@@

As $A\coworks B\equiv B'$, 
from \cref{lemma:cowinputmatch}
we know that $Q=Z$.

@@

We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
are at the beginning, and therefore 
from \cref{axiom:wrextpostfix}
$A\wrext \ordered{A\cap B}$ and by symmetry $B\wrext \ordered{A\cap B}$.
\end{proof}

@@

\begin{mylem}
If $S\coworks T$ and $\forall s\in S, t\in T: [s;t]\equiv[t;s]$
then $[S;T]\coworks S$.
In this case we also know
$\forall \FS: S\FS\neq\fsbroken \wedge T\FS\neq\fsbroken \Rightarrow [S;T]\FS\neq\fsbroken$
(but we can't yet express this in the algebra).
\end{mylem}

\begin{mylem}
$[S;T]\coworks[S;U]\Rightarrow T\coworks U$.
TODO Is this an axiom?
\end{mylem}

Turning back to reconciliation we know
$A\equiv[\ordered{A\cap B};A_0]$
where $A_0=\ordered{A\setminus B}$.
We define $B_0$ similarly.
As $A\coworks B$ we know $A_0\coworks B_0$.

We also know commands in $A_0$ and $\recb$ commute, that is,
$\forall a\in A_0, b\in\recb: [a;b]\equiv[b;a]$.
